Behavior Driven Development in Haskell

### 2012-05-30 paper.tex
adding filepath. adding a comment.

The standard documentation mechanism for Haskell is
Haddock.
Haddock has markup support for code blocks.  And it is widely used to
include properties and examples in documentation.

\begin{quote}
    sol: @kazu should we cite package documentation, to support this?
    I'm aware of:
    \begin{itemize}
        \item filepath
        \item containers
    \end{itemize}
\end{quote}

Here is an example from the {\tt containers} packages.

@@

\begin{quote}
    \emph{sol: I think the Haddock comment only contains properties.
    So the argumentation is shaky?}
\end{quote}

>>>>

The standard documentation mechanism for Haskell is
Haddock.
Haddock has markup support for code blocks.  And it is widely used to
include properties and examples in documentation.
For instance, the {\tt filepath} package and
the {\tt containers} package adopt this style.
Here is an example from the latter.

@@

\begin{quote}
    \emph{sol: I think the Haddock comment only contains properties.
    So the argumentation is shaky?} \\
    \emph{kazu: My point is that we cannot tell which the author of packages
   want to express, examples or properties.}
\end{quote}
